Adapting the Chumbley Score to match striae on Land Engraved Areas of bullets

### 2018-09-20 doc/paper.Rmd
update figures to percentages

p1 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=eer*100, colour=method, shape=method)) +
  geom_point(size=2) +
  facet_wrap(~wv, labeller = label_bquote(w[v] == .(wv))) + 
  theme_bw() +
  ylab("Equal Error (EER) in Percent") +
  xlab("Size of optimization window in pixels") +
  theme(legend.position = "bottom") + #c(0.25, 0.25)) +
  scale_colour_brewer("Method", palette="Set1") +
  scale_shape("Method") +
  scale_y_continuous(limits=c(0, 0.25))

@@

```{r type1, fig.width=7.75, fig.height=5.25, out.width='\\textwidth', fig.cap="Comparison of observed and nominal type I error rates  across a range of window sizes for optimization $wo$. The horizontal line in each facet indicates the nominal type I error rate."}
errorsCV$wv.method <- paste(errorsCV$method, errorsCV$wv, sep=" / ")
errorsCV %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = 100*actual, colour=factor(100*alpha), 
             linetype=method)) + 
  geom_hline(aes(yintercept=100*alpha), colour="grey30", size=.5) +
  geom_point(aes(shape=factor(wv.method)), size=2.5) +
  geom_smooth(aes(group=factor(method)), 
              size=.8, se=FALSE, method="lm", alpha=.9) +
  theme_bw() +
  ylab(expression("Observed Percent False Positives "~hat(alpha))) +
  xlab(expression("Window size for optimization "~w[o])) +
  scale_colour_brewer(
    expression("Nominal Percent False Positives "~alpha), palette="Set2") +
  facet_wrap(~alpha, labeller=label_bquote(alpha == .(alpha*100)), scales="free") +
  theme(legend.position="bottom") +
  scale_shape_manual(expression("Method / Validation window "~w[v]), values=c(1,2,16,17)) +
  scale_linetype_manual("Method", values=c(3,1), guide=FALSE) +
  guides(shape = guide_legend(ncol=2),
         col = guide_legend(ncol=2))

@@

```{r type2, fig.pos = 'h', fig.height = 3, fig.width = 7.5, out.width='0.9\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
ggerrors
```

>>>>

p1 <- roc.summary %>% filter(!(wo %in% c(130, 140))) %>%
  ggplot(aes( x = wo, y=eer*100, colour=method, shape=method)) +
  geom_point(size=2) +
  facet_wrap(~wv, labeller = label_bquote(w[v] == .(wv))) + 
  theme_bw() +
  ylab("Equal Error (EER) in Percent") +
  xlab("Size of optimization window in pixels") +
  theme(legend.position = "bottom") + #c(0.25, 0.25)) +
  scale_colour_brewer("Method", palette="Set1") +
  scale_shape("Method") +
  scale_y_continuous(limits=c(0, 25))

@@

```{r type1, fig.width=7.75, fig.height=5.25, out.width='\\textwidth', fig.cap="Comparison of observed and nominal type I error rates  across a range of window sizes for optimization $wo$. The horizontal line in each facet indicates the nominal type I error rate."}
errorsCV$wv.method <- paste(errorsCV$method, errorsCV$wv, sep=" / ")
errorsCV %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = 100*actual, colour=factor(100*alpha), 
             linetype=method)) + 
  geom_hline(aes(yintercept=100*alpha), colour="grey30", size=.5) +
  geom_point(aes(shape=factor(wv.method)), size=2.5) +
  geom_smooth(aes(group=factor(method)), 
              size=.8, se=FALSE, method="lm", alpha=.9) +
  theme_bw() +
  ylab(expression("Observed Percent False Positives "~hat(alpha))) +
  xlab(expression("Window size for optimization "~w[o])) +
  scale_colour_brewer(
    expression("Nominal Percent False Positives "~alpha), palette="Set2") +
  facet_wrap(~alpha, labeller=label_bquote(alpha == .(alpha*100)~'%'), scales="free") +
  theme(legend.position="bottom") +
  scale_shape_manual(expression("Method / Validation window "~w[v]), values=c(1,2,16,17)) +
  scale_linetype_manual("Method", values=c(3,1), guide=FALSE) +
  guides(shape = guide_legend(ncol=2),
         col = guide_legend(ncol=2))

@@

```{r type2, fig.pos = 'h', fig.height = 3, fig.width = 7.5, out.width='0.9\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 130$ we see a minimum in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
ggerrors # write our new?
```
